Behavior Driven Development in Haskell

### 2012-05-30 paper.tex
correcting wrong wording.

Many Haskell programmers tend not to write test code even though the
strong type system of Haskell cannot always ensure correct semantics.
Test code helps users to understand the usage of
functions and developers to maintain semantics
while extending software. To ease the production and enhance the value of test code, we
propose to carry out behavior driven development with two tools:
Doctest integrated with QuickCheck for user documentation and Hspec
with combinators extended for developer documentation. With our
method, specification can be used for documentation and automatic
testing. This kill-three-birds-with-one-stone aspect would motivate
Haskellers to write test code.

>>>>

Many Haskell programmers tend not to write test code even though the
strong type system of Haskell cannot always ensure correct semantics.
Test code helps users to understand the usage of
functions and developers to maintain semantics
while extending software. To ease the production and enhance the value of test code, we
propose to carry out behavior driven development with two tools:
Doctest integrated with QuickCheck for user documentation and Hspec
with combinators extended for code documentation. With our
method, specification can be used for documentation and automatic
testing. This kill-three-birds-with-one-stone aspect would motivate
Haskellers to write test code.
